---
title: "class09"
author: "Alina Kang"
date: "2/4/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## K-means clustering

The main k-means function in R is called 'kmeans()'. Let's play with it here.

```{r}
# Generate some example data for clustering
tmp <- c(rnorm(30,-3), rnorm(30,3))
x <- cbind(x=tmp, y=rev(tmp))

plot(x)
```


Use the kmeans() function setting k to 2 and nstart=20
```{r}
km <- kmeans(x, centers = 2, nstart = 20)
km
plot(x)

#Cluster size
km$cluster
```
```{r}
length(km$cluster)
table(km$cluster)
```

```{r}
plot(x, col = km$cluster)
points(km$centers, col="blue", pch=15, cex=3)

```


## Hierarchical clustering in R

The main Hierarchical clustering function in R is ca;;ed 'hclust()'
An important point here is that you have to calculate the distance matrix deom your input data befrore calling 'hclust()'

For this we will use the 'dist()' function first.

```{r}
# We will use our x again froma abive
d <- dist(x)
hc <- hclust(d)
hc
```

Folks often view the results of Hierarchical clustering graphically. Let's try passing this to the 'plot()' function.

```{r}
plot(hc)
```
```{r}
# Draws a dendrogram
plot(hc)
abline(h=6, col="red")
```


```{r}
plot(hc)
abline(h=6, col="red", lty = 2)
abline(h=4, col="blue")
```

To get cluster membership vector I need to "cut" the tree at a certain height to yield my separate cluster branches.

```{r}
cutree(hc, h=5)
```

```{r}
gp4 <- cutree(hc, k=6)
table(gp4)
```

```{r}
# Step 1. Generate some example data for clustering
x <- rbind(
 matrix(rnorm(100, mean=0, sd = 0.3), ncol = 2), # c1
 matrix(rnorm(100, mean = 1, sd = 0.3), ncol = 2), # c2
 matrix(c(rnorm(50, mean = 1, sd = 0.3), # c3
 rnorm(50, mean = 0, sd = 0.3)), ncol = 2))
colnames(x) <- c("x", "y")
```

```{r}
# Step 2. Plot the data without clustering
plot(x)
```

```{r}
# Step 3. Generate colors for known clusters
# (just so we can compare to hclust results)
col <- as.factor( rep(c("c1","c2","c3"), each=50) )
plot(x, col=col)
```

```{r}
cutree(hc, h=3)
hclust(dist(x))
```

```{r}
cutree(hc, h=6)
hclust(dist(x))
```


```{r}
plot(x)
```

```{r}
hc <- hclust(dist(x))
plot(hc)
abline(h=1.7, col="red")
cutree(hc, h=6)
```

```{r}
grps <- cutree(hc, k=3)
table(grps)
```


## PCA of UK food data
```{r}
x <- read.csv("UK_foods.csv", row.names = 1)
x


# Let's make some plotsto explore our data a bit more


barplot(as.matrix(x), beside=T, col=rainbow(nrow(x)))
```


Pair-wise plots
```{r}
pairs(x, col=rainbow(10), pch=16)
```

Principal Component Analysis (PCA) with the 'prcomp()' function.

```{r}
pca <- prcomp(t(x))
pca
#pca
```

What is my result object 'pca'? I cab check the attributes...
```{r}
attributes(pca)
```

```{r}
plot(pca$x[,1], pca$x[,2])
```

```{r}
summary(pca)
plot(pca$x[,1], pca$x[,2], xlab="PC1", ylab="PC2", xlim=c(-270,500))
text(pca$x[,1], pca$x[,2], colnames(x), col= c("black", "red", "blue", "darkgreen"))
```






















