---
title: "Class12: Structural Bioinformratics pt.1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PDB Statistics

Here we inspect the types of structures in the main database for 3D biomolecular data - the PDB.

> Q1: Determine the percentage of structures solved by X-Ray and Electron Microscopy.

> Download a CSV file from the PDB site (accessible from “Analyze” -> “PDB Statistics” >
“by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project
and determine the percentage of structures solved by X-Ray and Electron Microscopy. Also can
you determine what proportion of structures are protein? Aim to have a rendered GitHub
document with working code that yields your answers.

> Type HIV in the PDB website search box on the home page and determine how many
HIV-1 protease structures are in the current PDB?

```{r}
# read in file
stats <- read.csv("Data Export Summary.csv", row.names=1)

#Calculate percentage values for each 'method'
ans <- stats$Total / sum(stats$Total) * 100
names(ans) <- rownames(stats)
round(ans, 2)

```


> Q2: Also can you determine what proportion of structures are protein? Aim to have a rendered GitHub document with working code that yields your answers. 

```{r}
round(sum(stats$Proteins) / sum(stats$Total) * 100, 2)

```











