---
title: "Class06"
author: "Alina Kang"
date: "1/23/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
plot(1:5)
```


# Functions

## level 2 heading

### level 3 heading

lets see more about **file import** (i.e. reading files into R). The main read function in base R is`read.table()`


```{r}
read.table("test1.txt")
```

```{r}
read.table("test2.txt")
```

```{r}
read.table("test3.txt")
```

We need to add arguments to get this file imported

```{r}
t1 <- read.table("test1.txt", sep = ",", header = TRUE)
```

Or I could just use `read.csv()` which has the arguents I want in this case!
```{r}
t1 <- read.csv("test1.txt")
```

```{r}
t2 <- read.csv("test2.txt")
```

```{r}
t3 <- read.csv("test3.txt")
```

# Back to functions

Our first example

```{r}
add <- function(x, y=1) {
 # Sum the input x and y
 x + y
}
```

Let's try using this function
```{r}
add(7,3)
```

How doe sthis work with vectors as input
```{r}
add(c(1,2,4))
```
```{r}
add(c(1,2,4), 4)
```


What is this `range()` function?

```{r}
x <- c(4,4,10,3,11)
max(x)
min(x)
```





```{r}
rng <- range(x)
```
```{r}
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
```


```{r}
rescale(x)
```
```{r}
rescale(1:10)
```


```{r}
rescale( c(1,2,NA,3,10) )
```

```{r}
x <- c(1,2,NA,3,10)
rng <- range(x)
```


```{r}
rng <- range(x, no.rm = TRUE)
rng
```
```{r}
rescale2 <- function(x) {
  rng <- range(x, no.rm = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
}
```

```{r}
rescale2(c(1,2,NA,3,10))
```

rescale <- function(x, na.rm=TRUE, plot=FALSE) {
 rng <-range(x, na.rm=na.rm)
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 return(answer)
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
 return(answer)
}



```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```


hc <- hclust( dist( rbind(s1.b, s2.b, s3.b) ) )
plot(hc)


```{r}
s1 <- read.pdb("4AKE") # kinase with drug
s1
```
> Q1. What type of object is returned from `read.pdb()`

It is a list of 8 things and of class "pdb", "sse"
 

```{r}
class(s1)
```

```{r}
str(s1)
```

```{r}
s1$seqres
```


```{r}
aa321(s1$seqres)
```

```{r}
s1$atom
```

> Q2. What does the trim.pdb() function do?
  
It trims it down into a new, smaller PDB object, containing a subset of atoms, from a given larger PDB object.

> Q3.

> Q4.

> Q5. Which proteins are more similar to each other in their B-factor trends. How could you quantify this?

```{r}
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
points(s2.b, typ="l", ylab="Bfactor")
```


```{r}
hc <- hclust( dist( rbind(s1.b, s2.b, s3.b) ) )
plot(hc)
```

s1.b and s3.b are more similar to each other in their B-factor trends, as shown in the dendrogram above. They are closer to each other than the more distant protein, s2.b.


>Q6. How would you generalize the original code above to work with any set of input
protein structures? 

```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```


```{r}

```
```{r}
plot_colors <- c("cyan", "orange", "magenta")
```


```{r}
prot_drug <- function(file, chain, elmnt, fctr) {
  
  # Change the colors of the data in the graph
  plot_colors <- c("blue", "red", "black")
  
  
  # to iterate through every value of the file vector
  for (i in 1:length(file)) {
  s1 <- read.pdb(file[i])

  s1.chain <- trim.pdb(s1, chain = chain, elety = elmnt)
  
  atom_df <- s1.chain$atom
  
  # the "$" syntax cannot take a variable, so s1.fctr takes in all the atom information and selects an entire column based on the factor input
  s1.fctr <- atom_df[, fctr] 
  
  # First plot
  if (i == 1) {
    plotb3(s1.fctr, sse = s1.chain, typ = "l", ylab = paste(toupper(fctr), "factor", sep = ""), col = plot_colors[i])
    
    # Adding plots to the first plot
  } else {
    lines(s1.fctr, col = plot_colors[i])
  }
  }
  
  # Adding a legend to the graph
  legend("topright", title = "PDB File Name", file, fill = plot_colors, horiz=TRUE, cex = 0.5, inset = c(0.03, 0.06))
}
# Test with three files and the parameters chain A, carbon, and factor b.
files <- c("4AKE", "1AKE", "1E4Y")
chains <- "A"
elements <- "CA"
factors <- "b"

prot_drug(files, chains, elements, factors)
```













